---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
  knitr::opts_chunk$set(
    collapse = TRUE,
    comment = "#>",
    fig.path = "man/figures/README-",
    out.width = "100%"
)
```

# `{debtnetworkvisualizer}`

Visualize global debt networks based on World Bank International Debt Statistics (IDS). You can find a deployed version of the app at [app-debt-network-visualizer.tidy-intelligence.com](https://app-debt-network-visualizer.tidy-intelligence.com/)

## Installation

You can install the development version of `{debtnetworkvisualizer}` like so:

```{r, eval = FALSE}
pak::pak("tidy-intelligence/app-debt-network-visualizer")
```

## Run

You can launch the application by running:

```{r, eval = FALSE}
debtnetworkvisualizer::run_app()
```

## About

You are reading the doc about version : `r golem::pkg_version()`

This README has been compiled on the

```{r}
Sys.time()
```

Here are the tests results and package coverage:

```{r, error = TRUE}
devtools::check(quiet = TRUE)
```

```{r echo = FALSE}
unloadNamespace("debtnetworkvisualizer")
```
